Generality in food webs scales with species richness, not latitude

### 2015-04-09 manuscript/latitudepaper.tex
Updated all results

[[Not redone yets]]

Link density, generality, and vulnerability each increased with increasing species richness ($\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675, $p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001). 
For estuarine, marine, and terrestrial food webs this increase did not vary with latitude ($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354; and $\beta_{Latitude}$=-0.001, $p$=0.334)

The strength of
this increase varied both over latitude and across ecosystem types. For $Z$,
scaling was stronger towards the equator except in lake ecosystems where scaling was stronger
towards the poles (Fig.~\ref{LS}). $G$ and $V$ followed the same trends, except that scaling of $G$
with $S$ was stronger towards the poles as in lakes (Figs.~\ref{Gen, Vul}).

When considering the proportion of $S$ accounted for by different trophic
levels, however, the scaling relationships with $Z$, $G$, and $V$ were more
complex. While $Z$ increased with increasing $I$ as well as with increasing
$S$, $Z$ tended to decrease with increasing $B$ and $T$. The decrease of $Z$
with $B$ was stronger towards the poles in estuarine, lake, and stream webs
(), varied little over latitude in marine webs (), and was stronger towards
the poles in terrestrial webs (). The best-fitting model for the relationship
of $Z$ and $I$ did not include any terms for variation in scaling across
latitude for any ecosystem type. Similar to the scaling of $Z$ with $B$, the
decrease in $Z$ with increasing $T$ was stronger towards the poles in
estuarine, lake, and marine webs, although the influence of latitude was
weaker than with $B$ (). Again like the relationship between $Z$ and $B$,
scaling of $Z$ with $T$ was stronger towards the equator in terrestrial webs.
Unlike in the relationship between $Z$ and $B$, however, scaling of $Z$ with
$T$ was also stronger towards the equator in stream webs.

As with $Z$, $G$ tended to decrease with increasing $B$ and $T$ and increase
with increasing $I$. Once again, however, these trends varied with latitude
and ecosystem type. The decline of G with increasing S was strongest at the
poles in estaurine, lake, and marine ecosystems; in each ecosystem type $G$
increased slightly with $B$ in equatorial webs. In marine webs $G$ increased
slightly with $B$ at all latitudes and in terrestrial webs $G$ increased with
$B$ in high-latitude webs but decreased slightly with $B$ at the equator. The
strength of the increase in $G$ with $I$ varied little with latitude except in
stream webs, where the increase was strongest towards the equator and $G$
decreased with $I$ in arctic food webs. The best-fitting model for the scaling
of $G$ with $T$ did not include any terrms for latitude in any ecosystem type.

$V$ too generally decreased with increasing $B$ and $T$ while increasing with
$I$. Similar to $G$, the decline of $V$ with increasing $B$ was strongest
towards the poles in estuarine, lake, and stream webs, varied little with
latitude in marine webs, and was strongest towards the equator in terrestrial
food webs. As with $Z$, the best-fit model for the scaling of $V$ with $I$ did
not include any terms for latitude in any ecosystem type. Scaling of $V$ with
$T$ was also simmilar to the pattern for $Z$, with sharper decreases in $V$
towards the poles in estuarine, lake, and marine webs and stronger towards the
equator in terrestrial and stream webs.

@@

\begin{figure}[!h]
\label{S}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
\caption{}
\end{figure}

>>>>

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354;
and $\beta_{Latitude}$=-0.001, $p$=0.334). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.004, $p$=; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs, only the strength of scaling of generality increased with
latitude ($\beta_{Latitude}$=0.007, $p$=0.002).

In general, link density, generality, and vulnerability decreased as the
proportion of basal resources in a web increased (Fig.~\ref{B}). For
estuarine, lake, and stream food webs these decreases were steeper towards the
poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
$\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
$\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
In marine food webs there was very little effect of latitude on
the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
$\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
while in terrestrial food webs scaling was stronger towards the 
equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
$\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).

In contrast to the proportion of basal resources, link density, generality,
and vulnerability tended to increase with increasing proportions of
intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
density and vulnerability with the proportion of intermediate consumers did
not include any effect of latitude on scaling in any ecosystem type. Scaling
of generality was stronger towards the equator in estuarine, lake, marine, and
stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
$p$=0.053). In lake and stream food webs, generality increased more weakly
with the proporiton of intermediate consumers such that, at low proportions,
the effect of latitude could negate or reverse the increase.

As with the proportion of basal resources, link density, generality, and
vulnerability decreased as the proportion of top predators increased. For
estuarine, lake, and marine food webs scaling of link density, generality, and
vulnerability did not vary significantly with latitude
($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
generality did not include any terms for latitude in any ecosystem type). In
stream and terrestrial food webs, the decrease in link density and
vulnerability was steeper towards the poles, although this trend was
significant only in streams ($\beta_{Latitude:Stream}$=0.015,
$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).

@@

\begin{figure}[!h]
\label{S}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
\caption{}
\end{figure}
